Bip32-Ed25519++: A More Secure Hierarchical Deterministic Wallet Standard for Ed25519 Keys

### 2024-05-16 paper.tex
fix quotation marks

The terms "account" and "address" are sometimes used interchangeably in casual conversation. In the HD wallet context however, an address is the most basic unit, while an account represents a logical grouping of many addresses.

@@

An alternate elliptic curve standard for digital signatures is Ed25519\cite{Ed25519}. It is used by a number of blockchains such as Algorand\cite{AlgorandEd25519}, Cardano\cite{CardanoEd25519}, Monero\cite{MoneroEd25519}, Nano\cite{NanoEd25519}, Solana\cite{SolanaEd25519} and more. Polkadot\cite{PolkadotEd25519} uses a variant called Schnorrkel/Ristretto x25519 ("sr25519") and Tezos\cite{TezosEd25519} offers it alongside other curves.

@@

While solving the problem (with only minor modifications to BIP32 and working with "after-hash" private keys of Ed25519)\cite{BIP32-Ed25519}, certain decisions were made that result in unnecessary security degradation.

@@

>>>>

The terms ``account'' and ``address'' are sometimes used interchangeably in casual conversation. In the HD wallet context however, an address is the most basic unit, while an account represents a logical grouping of many addresses.

@@

An alternate elliptic curve standard for digital signatures is Ed25519\cite{Ed25519}. It is used by a number of blockchains such as Algorand\cite{AlgorandEd25519}, Cardano\cite{CardanoEd25519}, Monero\cite{MoneroEd25519}, Nano\cite{NanoEd25519}, Solana\cite{SolanaEd25519} and more. Polkadot\cite{PolkadotEd25519} uses a variant called Schnorrkel/Ristretto x25519 (``sr25519'') and Tezos\cite{TezosEd25519} offers it alongside other curves.

@@

While solving the problem (with only minor modifications to BIP32 and working with ``after-hash'' private keys of Ed25519)\cite{BIP32-Ed25519}, certain decisions were made that result in unnecessary security degradation.

@@

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
